GEE models

### 2017-07-01 doc/manuscript.Rmd
removed activity questionnaire description in methods

Height, weight, and waist circumference (WC) were measured at all clinic 
examinations using standard procedures.  WC was measured at the natural waist, 
defined as the narrowest part of the torso between the umbilicus and the xiphoid
process. BMI was calculated by dividing weight (kg) by height (m) squared.
Sociodemographic information, including age, sex, and ethnicity, were determined
using questionnaires administered at each examination. In the lifestyle
questionnaire, physical activity was determined using a version of the
Modifiable Activity Questionnaire (MAQ) [@Kriska1990].  The MAQ collects 
information on leisure and occupational activity, including intensity, 
frequency, and duration, over the past year.  Each reported activity from the 
MAQ was weighted by its metabolic intensity allowing for the estimation of 
MET-hours per week.

>>>>

Height, weight, and waist circumference (WC) were measured at all clinic 
examinations using standard procedures.  WC was measured at the natural waist, 
defined as the narrowest part of the torso between the umbilicus and the xiphoid
process. BMI was calculated by dividing weight (kg) by height (m) squared.
Sociodemographic information, including age, sex, and ethnicity, were determined
using questionnaires administered at each examination.
